---
title: "`r Sys.getenv('PROJ_TITLE')`"
subtitle: 0.0.0.9000
description: "`r Sys.getenv('PROJ_DESCRIPTION')`"
author:
  - name: A. Uthor
    orcid_id: "0000-0002-0520-7428"
    affiliation: Zeta Research S.R.L
    affiliation_url: https://www.zetaresearch.com
  - name: Corrado Lanera
    url: https://CorradoLanera.it
    orcid_id: "0000-0002-0520-7428"
    affiliation: Unit of Biostatistics, Epidemiology, and Public Health
    affiliation_url: https://www.unipd-ubep.it/
  - first_name: Federica
    last_name: Zobec
    affiliation: Zeta Research S.R.L
    affiliation_url: https://www.zetaresearch.com
citation_url: https://github.com/zeta-r/
date: "`r Sys.Date()`"
bibliography: biblio.bib
preview: man/img/logo.png
slug: "report_v00.00.00_CL"
twitter:
  site: "ZetaResearch"
  creator: "CorradoLanera"
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    theme: zeta.css
---

<!-- DON'T RENDER THE REPORT BY HAND DIRECTLY! -->
<!-- use `dev/03-run_cycle.R` script to trigger it instead -->


```{r setup, include=FALSE}
options(
  width = 150,
  tidyverse.quiet = TRUE
)

knitr::opts_chunk$set(
  echo = FALSE,
  comment = "",
  collapse = TRUE,
  warning = FALSE,
  out.width  = "100%",   # part of output covered
  dpi = 300,             # set output resolution (impact weight)
  fig.width = 16, fig.height = 9
)

suppressPackageStartupMessages({
  library(depigner)
  library(fontawesome)
  library(glue)
  library(gt)
  library(here)
  
  library(pander)
    panderOptions('knitr.auto.asis', FALSE)
    panderOptions("round", 2)
    panderOptions("table.split.table", Inf)
    panderOptions(
      "table.alignment.default",
      function(df) c("left", rep("center", length(df) - 1L))
    )
    
  library(rms)
    options(datadist = "dd")
  
  library(tarchetypes)
  library(tidyverse)
  


})


htmltools::img(
 src = knitr::image_uri(here("man", "img", "logo.png")),
 alt = 'logo',
 style = 'position:absolute; top:0; right:0; padding:10px;'
 )
fa_html_dependency()

list.files(here("R"), pattern = "\\.R$", full.names = TRUE) |>
  lapply(source) |> invisible()
```


::: l-body-outset
| **Titolo del progetto**:|  **PROJ - REPORT**           |
|-------------------------|-----------------------------------------|
| **Richiesta**:          | Analisi statistica                      |
| **Committente**:        | XXXXX                                   |
| **Analisi Statistica**: | Corrado Lanera, Zeta Research S.R.L.    |
:::


```{r tab-rev, layout = "l-body-outset"}
tribble(
  ~ `EDIZIONE N  `, ~ `REVISIONE N  `, ~ DATA       , ~ `MOTIVAZIONE DELLA REVISIONE`,
  "01"    ,       "00"     , "2000-01-01" , "Prima edizione"
) %>%
  gt() %>%
  tab_header(
    title = "STORIA DELLE REVISIONI REPORT",
    subtitle = glue::glue("Progetto: PROJ - REPORT")
  ) %>%
  fmt_date(
    columns = c(DATA),
    date_style = 3
  )
```




## Project status

```{r, message=FALSE, echo=FALSE, layout = "l-screen", out.height="400px"}
targets::tar_visnetwork(
  # targets_only = TRUE,
  exclude = c(
    "report", all_of(extract_fct_names(here::here("R/utils.R"))),
    starts_with(".get")
  )
)
```



## Introduction

<aside>
This content will appear in the gutter of the article.
</aside>

## Methods

Footnotes use standard Pandoc markdown notation, for example ^[This will become a hover-able footnote]. The number of the footnote will be automatically generated.

## Analyses

Here just `tar_read()` your target objects and comment it!

## Results


You can get the results of your analyses as well by

```{r}
str(tar_read(relevantResults), 1)
```


## Discussion

Lorem ipsum


## Acknowledgments {.appendix}

This is a place to recognize people and institutions. It may also be a good place to acknowledge and cite software that makes your work possible.

## Author Contributions {.appendix}

We strongly encourage you to include an author contributions statement briefly describing what each author did.





## Environment {.appendix}

<details>
  <summary>Session info</summary>
```{r, results='markup'}
devtools::session_info()
```
</details>


